Revised Time Complexity Analysis of Solving TSP with Genetic Algorithms Including the Number of Cities

### 2024-02-05 latex/ESWA_complexity.tex
Time complexity updated

Load $K$ lines of text to compose a distances matrix for $K$ airports, the $m$ packed contents from previous nodes, and $n$ items parameters from text files are of complexities $O(K)$, $O(m)$, and $O(n)$, respectively:

	\begin{itemize}
		\item $O(K + m + n)$
	\end{itemize}

@@

\begin{itemize}
\item If $K <= 6$, determine the number of tours through permutation. To get permutation of nodes as tours has a complexity of $O(T = K! \cdot K)$, as the number of nodes is permutated (factorial) to generate tours.

	\begin{itemize}
	\item $ O(K + m + n) + O(T = K! \cdot K)$ or
	\item $ O(K + m + n) + O(T = 2)$, if the we are solving the two optimal TSP tours.
	\end{itemize}

@@

	\begin{itemize}
		\item $O(K + m + n) + O(T = 100)$
	\end{itemize}
\end{itemize}

@@

\begin{itemize}
	\item $O(K + m + n) + O(T)$
\end{itemize}

a) each tour with $K$ nodes:
\begin{itemize}
	\item $O(K + m + n) + O(T \cdot K)$
\end{itemize}

b) in each node we have to reset (to eliminate the risk of previous destinations assigned to a pallet) $O(K \cdot m)$ and set the empty pallets destinations: $O(K \cdot m + K \cdot m) = O(2 \cdot K \cdot m) = O(K \cdot m)$
\begin{itemize}
	\item $O(K + m + n) + O(T \cdot K \cdot (K \cdot m))$
\end{itemize}

c) To calculate the time limit to solve each node, it is necessary to determine the potential total volume for each node.: $O(K \cdot n)$
\begin{itemize}
	\item $O(K + m + n) + O(T \cdot K \cdot (K \cdot m + K \cdot n))$
\end{itemize}

d) The time complexity to put the packet contents destined to the next nodes in the tour on board: $O(m)$.
\begin{itemize}
	\item $O(K + m + n) + O(T \cdot K \cdot (K \cdot m + K \cdot n + m))$
\end{itemize}

d) The time complexity to optimize the pallets positions to minimize the CG deviation: $O(m^2)$ ($m$ pallets in $m$ positions)
\begin{itemize}
	\item $O(K + m + n) + O(T \cdot K \cdot (K \cdot m + K \cdot n + m + m^2))$
\end{itemize}

e) Plus the time complexity of the method used to solve an ACLPP with the aircraft partially loaded: $O(C)$
\begin{itemize}
	\item $O(K + m + n) + O(T \cdot K \cdot (K \cdot m + K \cdot n + m + m^2 + C))$
\end{itemize}

\subsubsection{Considering the Shims algorithm: $O(C) = O(Shims)$}

a) the time complexity for sorting the pallets in non-descending order of distances to the CG:
\begin{itemize}
	\item $O(Shims) = m \cdot log(m)$
\end{itemize}

b) As each pallet is solved at a time, the overall Shims complexity is multiplied by $m$.
\begin{itemize}
	\item $O(Shims) = m.(m \cdot log(m))$
\end{itemize}

c) The greedy phase has $O(n)$.
\begin{itemize}
	\item $O(Shims) = m \cdot (m \cdot log(m) + n)$
\end{itemize}

d) The composition phase has $O(n)$ added to the First-Fit Decreasing algorithm time complexity $O(m \cdot log(m))$
\begin{itemize}
	\item $O(Shims) = m \cdot (m \cdot log(m) + n + n + m \cdot log(m))$
	\item $O(Shims) = m \cdot (2n + 2 \cdot m \cdot log(m)) = m \cdot (n + m \cdot log(m))$
\end{itemize}

The overall time complexity to solve the ACLP+RPDP with Shims is:
\begin{itemize}
	\item $O(K+m+n) + O(T \cdot K \cdot (K \cdot m + K \cdot n + m + m^2 + m \cdot (n + m \cdot log(m))))$
\end{itemize}

The overall time complexity provided combines two distinct parts: $O(K+m+n)$ and $O(T \cdot K \cdot (K \cdot m + K \cdot n + m + m^2 + m \cdot (n + m \cdot \log(m))))$. Analysing each part separately and then considering their combined implications provides insight into the algorithm's performance characteristics.

@@

\textbf{First Part:} $O(K+m+n)$

@@

\textbf{Second Part:} $O(T \cdot K \cdot (K \cdot m + K \cdot n + m + m^2 + m \cdot (n + m \cdot \log(m))))$

@@

When combining these parts, the linear terms in the first part ($O(K+m+n)$) are overshadowed by the more complex and potentially rapidly increasing terms of the second part, especially due to the presence of $m^2$ and the product $T \cdot K \cdot (...)$. The quadratic ($m^2$) and logarithmic ($m \cdot \log(m)$) terms indicate that the algorithm's efficiency decreases significantly as the number of pallets $m$ increases.

@@

Given these parameters, we can express the overall time complexity as:
\begin{itemize}
	\item $O(G \cdot (P \cdot (S(K) + P \cdot (C(K) + M(K)))))$
\end{itemize}

>>>>

Load $K$ lines of text to compose a distances matrix for $K$ airports, the $m$ packed contents from previous nodes, and $n$ items parameters from text files are of complexities $\mathcal{O}(K)$, $\mathcal{O}(m)$, and $\mathcal{O}(n)$, respectively:

	\begin{itemize}
		\item $\mathcal{O}(K + m + n)$
	\end{itemize}

@@

\begin{itemize}
\item If $K <= 6$, determine the number of tours through permutation. To get permutation of nodes as tours has a complexity of $\mathcal{O}(T = K!)$, as the nodes are permutated (factorial) to generate tours.

	\begin{itemize}
	\item $ \mathcal{O}(K + m + n) + \mathcal{O}(T = K!)$ or
	\item $ \mathcal{O}(K + m + n) + \mathcal{O}(T = 2)$, if the we are solving the two optimal TSP tours.
	\end{itemize}

@@

	\begin{itemize}
		\item $\mathcal{O}(K + m + n) + \mathcal{O}(T = 100)$
	\end{itemize}
\end{itemize}

@@

\begin{itemize}
	\item $\mathcal{O}(K + m + n) + \mathcal{O}(T)$
\end{itemize}

a) For each tour with $K$ nodes:
\begin{itemize}
	\item $\mathcal{O}(K + m + n) + \mathcal{O}(T \cdot K)$
\end{itemize}

b) in each node we have to reset (to eliminate the risk of previous destinations assigned to a pallet) $\mathcal{O}(K \cdot m)$ and set the empty pallets destinations: $\mathcal{O}(K \cdot m + K \cdot m) = \mathcal{O}(2 \cdot K \cdot m) = \mathcal{O}(K \cdot m)$
\begin{itemize}
	\item $\mathcal{O}(K + m + n) + \mathcal{O}(T \cdot K \cdot (K \cdot m))$
\end{itemize}

c) To calculate the time limit to solve each node, it is necessary to determine the potential total volume for each node.: $\mathcal{O}(K \cdot n)$
\begin{itemize}
	\item $\mathcal{O}(K + m + n) + \mathcal{O}(T \cdot K \cdot (K \cdot m + K \cdot n))$
\end{itemize}

d) The time complexity to put the packet contents destined to the next nodes in the tour on board: $\mathcal{O}(m)$.
\begin{itemize}
	\item $\mathcal{O}(K + m + n) + \mathcal{O}(T \cdot K \cdot (K \cdot m + K \cdot n + m))$
\end{itemize}

d) The time complexity to optimize the pallets positions to minimize the CG deviation: $\mathcal{O}(m^2)$ ($m$ pallets in $m$ positions)
\begin{itemize}
	\item $\mathcal{O}(K + m + n) + \mathcal{O}(T \cdot K \cdot (K \cdot m + K \cdot n + m + m^2))$
\end{itemize}

e) Plus the time complexity of the method used to solve an ACLPP with the aircraft partially loaded: $\mathcal{O}(C)$
\begin{itemize}
	\item $\mathcal{O}(K + m + n) + \mathcal{O}(T \cdot K \cdot (K \cdot m + K \cdot n + m + m^2 + C))$
\end{itemize}

\subsubsection{Considering the Shims algorithm: $\mathcal{O}(C) = \mathcal{O}(Shims)$}

a) the time complexity for sorting the pallets in non-descending order of distances to the CG:
\begin{itemize}
	\item $\mathcal{O}(Shims) = m \cdot log(m)$
\end{itemize}

b) As each pallet is solved at a time, the overall Shims complexity is multiplied by $m$.
\begin{itemize}
	\item $\mathcal{O}(Shims) = m.(m \cdot log(m))$
\end{itemize}

c) The greedy phase has $\mathcal{O}(n)$.
\begin{itemize}
	\item $\mathcal{O}(Shims) = m \cdot (m \cdot log(m) + n)$
\end{itemize}

d) The composition phase has $\mathcal{O}(n)$ added to the First-Fit Decreasing algorithm time complexity $\mathcal{O}(m \cdot log(m))$
\begin{itemize}
	\item $\mathcal{O}(Shims) = m \cdot (m \cdot log(m) + n + n + m \cdot log(m))$
	\item $\mathcal{O}(Shims) = m \cdot (2n + 2 \cdot m \cdot log(m)) = m \cdot (n + m \cdot log(m))$
\end{itemize}

The overall time complexity to solve the ACLP+RPDP with Shims is:
\begin{itemize}
	\item $\mathcal{O}(K+m+n) + \mathcal{O}(T \cdot K \cdot (K \cdot m + K \cdot n + m + m^2 + m \cdot (n + m \cdot log(m))))$
\end{itemize}

The overall time complexity provided combines two distinct parts: $\mathcal{O}(K+m+n)$ and $\mathcal{O}(T \cdot K \cdot (K \cdot m + K \cdot n + m + m^2 + m \cdot (n + m \cdot \log(m))))$. Analysing each part separately and then considering their combined implications provides insight into the algorithm's performance characteristics.

@@

\textbf{First Part:} $\mathcal{O}(K+m+n)$

@@

\textbf{Second Part:} $\mathcal{O}(T \cdot K \cdot (K \cdot m + K \cdot n + m + m^2 + m \cdot (n + m \cdot \log(m))))$

@@

When combining these parts, the linear terms in the first part ($\mathcal{O}(K+m+n)$) are overshadowed by the more complex and potentially rapidly increasing terms of the second part, especially due to the presence of $m^2$ and the product $T \cdot K \cdot (...)$. The quadratic ($m^2$) and logarithmic ($m \cdot \log(m)$) terms indicate that the algorithm's efficiency decreases significantly as the number of pallets $m$ increases.

So, the overall time complexity may be simplified by relaxing the first part to:
\begin{itemize}
	\item $\mathcal{O}(T \cdot K \cdot (K \cdot m + K \cdot n + m + m^2 + m \cdot (n + m \cdot log(m))))$
\end{itemize}

@@

Given these parameters, we can express the overall time complexity as:
\begin{itemize}
	\item $\mathcal{O}(G \cdot (P \cdot (S(K) + P \cdot (C(K) + M(K)))))$
\end{itemize}
